Multi-Instance Methods for Partially Supervised Image Segmentation

### 2013-09-18 partial_supervision/paper.tex
slightly better related work for weakly supervised.

\subsection{Semantic Scene Segmentation using Weak Annotation }
Recently, several methods have been proposed to obtain semantic segmentations
of images using only image-level
supervision~\citep{vezhnevets2011weakly,verbeek2007region,vezhnevets2010towards}.
\citet{vezhnevets2011weakly}, for example, report impressive results on the
MSRC dataset.

>>>>

\subsection{Semantic Scene Segmentation using Weak Annotation}
Learning semantic segmentation from image-level annotation was first investigated in \citet{verbeek2007region},
using a semi-supervised conditional random field on patches. \citet{verbeek2007region} evaluated their approach
on the MSRC-9 datasets.
More recently, simliar approaches were proposed by
\citet{vvezhnevets2011weakly} and \citet{vezhnevets2010towards}.
\citet{vezhnevets2011weakly} independently developed a multiple-instance based
approach to segmentation, and report impressinve results on the MSRC-21 dataset.
